full title

### 2020-09-09 paper/pldi21/detail.tex
[PLDI21] Removed unnecessary files / Updated formalization

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

>>>>

\section{Application: JavaScript}

\todo

% \subsection{Core Language}
% \[
%   \begin{array}{ll@{~}c@{~}l}
%     \text{Programs} & \prog &::=& (\lab: \inst)^*\\
%     \text{Labels} & \lab &\in& \labset\\
%     \text{Instructions} & \inst &::=& x = \expr \mid \kwif \; \expr \; \lab \;
%     \lab\\
%     \text{Expressions} & \expr &::=& \const \mid x \mid \op(\expr, \cdots,
%     \expr)\\
%   \end{array}
% \]
% 
% In a core language, we define a program as a sequence of labelled instructions
% and instructions are variable assignments and branches.  An expression is a
% constant $\const$, a variable $x$, and $n$-ary operations.  We define states
% $\stset = \labset \times \memset$ as pairs of labels and memories mapping from
% variables to values.  We define the transition relation $\trans$ between states
% as follows:
% 
% \begin{prooftree}
%   \AxiomC{$\prog = \cdots, \lab: x = \expr, \lab': \inst, \cdots$}
%   \AxiomC{$\sem{e}(\mem) = v$}
%   \BinaryInfC{$(\lab, \mem) \trans (\lab', \mem[x \mapsto v])$}
% \end{prooftree}

### 2020-09-09 paper/pldi21/formal.tex
[PLDI21] Removed unnecessary files / Updated formalization

\subsection{Notation}
\[
  \begin{array}{ll@{~}c@{~}l}
    \text{Programs} & \prog &::=& (\lab: \inst)^*\\
    \text{Labels} & \lab &\in& \labset\\
    \text{Instructions} & \inst &::=& x = \expr \mid \kwif \; \expr \; \lab \;
    \lab \mid \cdots\\
    \text{Expressions} & \expr &::=& \const \mid x \mid \lambda x. \lab \mid \op(\expr, \cdots, \expr)
    \mid \cdots\\
  \end{array}
\]

\subsection{Concrete Semantics}

We represent the semantics of a program $\prog$ as a state transition system
$(\stset, \trans, \istset)$.  A state $\st \in \stset$ represents a status of the
program $\prog$ and $\istset$ denotes the initial state set.  The transition
relation $\trans \subseteq \stset \times \stset$ describes how states are
transformed to other states.

A \textit{collecting semantics} $\sem{\prog} = \{ \st \in \stset \mid \ist \in
\istset \wedge \ist \trans^* \st \}$ consists of reachable states from initial
states of the program $\prog$.  We could calculate it using the \textit{transfer
function} $\transfer: \dom \rightarrow \dom$ as follows:
\[
  \begin{array}{r@{~}c@{~}l}
    \sem{\prog} &=& \underset{n \rightarrow \infty}{\lim}{\transfer^n(\ielem)}\\
    \transfer(\elem) &=& \elem \join \step(\elem)\\
  \end{array}
\]
The \textit{concrete domain} $\dom = \powerset{\stset}$ is a complete lattice
with $\cup$, $\cap$, and $\subseteq$ as its join($\join$), meet($\meet$), and
partial order($\order$) operators.  The initial states are $\ielem = \istset$.
The \textit{one-step execution} $\step: \dom \rightarrow \dom$ transforms states
using the transition relation $\trans$: $\step(\elem) = \{ \st' \mid \st \in
\elem \wedge \st \trans \st' \}$.

\subsection{Abstract Interpretation}
The abstract interpretation over-approximate the transfer $\transfer$ to the
\textit{abstract transfer function} $\abstransfer: \absdom \rightarrow \absdom$
to get the \textit{abstract semantics} $\abssem{\prog}$ in finite iterations as
follows:
\[
    \abssem{\prog} = \underset{n \rightarrow
    \infty}{\lim}{(\abstransfer)^n(\iabselem)}\\
\]
We define a \textit{state abstraction} $\dom \galois{\alpha}{\gamma} \absdom$ as
a Galois connection between the concrete domain $\dom$ and an abstract domain
$\absdom$ with a \textit{concretization function} $\gamma$ and a
\textit{abstraction function} $\alpha$.  The initial abstract state $\iabselem
\in \absdom$ represents an abstraction of the initial state set; $\ielem
\subseteq \gamma(\iabselem)$.  The abstract transfer function $\abstransfer:
\absdom \rightarrow \absdom$ is defined as $\abstransfer(\abselem) = \abselem
\join \absstep(\abselem)$ with an \textit{abstract one-step execution}
$\absstep: \abselem \rightarrow \abselem$.  For the sound state abstraction, the
join operator and the abstract one-step execution should satisfy the following
conditions:
\begin{itemize}
  \item $\forall \abselem_0, \abselem_1 \in \absdom. \; \gamma(\abselem_0) \cup
    \gamma(\abselem_1) \subseteq \gamma(\abselem_0 \join \abselem_1)$
  \item $\forall \abselem \in \absdom. \; \absstep \circ \gamma(\abselem) \subseteq
    \gamma \circ \absstep(\abselem)$
\end{itemize}

>>>>

\subsection{Concrete Semantics}
\[
  \prog ::= (\lab: \inst)^*\\
\]
A program $\prog$ is a sequence of labelled instructions.  We represent the
semantics of a program $\prog$ as a state transition system $(\stset, \trans,
\istset)$.  A state $\st \in \stset = \labset \times \memset$ is a pair of a
label and a memory and represents a status of the program $\prog$.  A memory
$\mem \in \memset = \locset \finmap \valset$ is a finite mapping from locations
to values. A program starts with an initial state in $\istset$.  The transition
relation $\trans \subseteq \stset \times \stset$ describes how states are
transformed to other states.

A \textit{collecting semantics} $\sem{\prog} = \{ \st \in \stset \mid \ist \in
\istset \wedge \ist \trans^* \st \}$ consists of reachable states from initial
states of the program $\prog$.  We could calculate it using the \textit{transfer
function} $\transfer: \dom \rightarrow \dom$ as follows:
\[
  \sem{\prog} = \underset{n \rightarrow \infty}{\lim}{\transfer^n(\ielem)}\\
  \qquad
  \transfer(\elem) = \elem \join \step(\elem)\\
\]
The \textit{concrete domain} $\dom = \powerset{\stset}$ is a complete lattice
with $\cup$, $\cap$, and $\subseteq$ as its join($\join$), meet($\meet$), and
partial order($\order$) operators.  The initial states are $\ielem = \istset$.
The \textit{one-step execution} $\step: \dom \rightarrow \dom$ transforms states
using the transition relation $\trans$: $\step(\elem) = \{ \st' \mid \st \in
\elem \wedge \st \trans \st' \}$.

\subsection{Abstract Interpretation}
The abstract interpretation over-approximate the transfer $\transfer$ to the
\textit{abstract transfer function} $\abstransfer: \absdom \rightarrow \absdom$
to get the \textit{abstract semantics} $\abssem{\prog}$ in finite iterations as
follows:
\[
    \abssem{\prog} = \underset{n \rightarrow
    \infty}{\lim}{(\abstransfer)^n(\iabselem)}\\
\]
We define a \textit{state abstraction} $\dom \galois{\alpha}{\gamma} \absdom$ as
a Galois connection between the concrete domain $\dom$ and an abstract domain
$\absdom$ with a \textit{concretization function} $\gamma$ and a
\textit{abstraction function} $\alpha$.  The initial abstract state $\iabselem
\in \absdom$ represents an abstraction of the initial state set; $\ielem
\subseteq \gamma(\iabselem)$.  The abstract transfer function $\abstransfer:
\absdom \rightarrow \absdom$ is defined as $\abstransfer(\abselem) = \abselem
\join \absstep(\abselem)$ with an \textit{abstract one-step execution}
$\absstep: \absdom \rightarrow \absdom$.  For the sound state abstraction, the
join operator and the abstract one-step execution should satisfy the following
conditions:
\begin{itemize}
  \item $\forall \abselem_0, \abselem_1 \in \absdom. \; \gamma(\abselem_0) \cup
    \gamma(\abselem_1) \subseteq \gamma(\abselem_0 \join \abselem_1)$
  \item $\forall \abselem \in \absdom. \; \absstep \circ \gamma(\abselem) \subseteq
    \gamma \circ \absstep(\abselem)$
\end{itemize}

\subsection{Analysis Sensitivity}

Abstract interpretation is often defined with \textit{analysis sensitivity} to
increase the precision of static analysis.  A sensitive abstract domain
$\sabsdom: \viewset \rightarrow \absdom$ is defined with a \textit{view
abstraction} $\viewmap: \viewset \rightarrow \dom$ that provides multiple points
of views for reachable states during static analysis.  It maps a finite number
of views $\viewset$ to sets of states $\dom$. Each view $\view \in \viewset$
represents a set of states $\viewmap(\view)$.
A \textit{sensitive state abstraction} $\dom
\galois{\alpha_\viewmap}{\gamma_\viewmap} \sabsdom$ is a Galois connection between
the concrete domain $\dom$ and the sensitive abstract domain $\sabsdom$ with the
following concretization function:
\[
  \gamma_\viewmap(\abselem) = \{ \st \in \stset \mid \forall \view \in \viewset.
  \; \st \in \viewmap(\view) \Rightarrow \st \in \gamma \circ \sabselem(\view) \}
\]

With analysis sensitivities, the abstract one-step execution $\sabsstep:
\sabsdom \rightarrow \sabsdom$ is defined as follows:
\[
  \sabsstep(\sabselem) = \lambda \view \in \viewset. \; \underset{\view' \in
  \viewset}{\bigjoin}{\viewtrans{\view'}{\view} \circ \sabselem(\view')}
\]
where $\viewtrans{\view'}{\view}: \absdom \rightarrow \absdom$ is the abstract
semantics of a \textit{view transition} from a view $\view'$ to another view
$\view$.  It should satsify the following condition for the soundness of the
analysis:
\[
  \forall \abselem \in \absdom. \; \step(\gamma(\abselem) \cap \viewmap(\view'))
  \cap \viewmap(\view) \subseteq \gamma \circ
  \viewtrans{\view'}{\view}(\abselem)
\]

One of the most widely-used sensitivity techniques is \textit{flow sensitivity}
using a flow sensitive view abstraction $\fsviewmap: \labset \rightarrow \dom$.
It discriminates states using their labels as follows:
\[
  \forall \lab \in \labset. \; \fsviewmap(\lab) = \{ \st \in \stset \mid \st =
  (\lab, \_) \}
\]

\subsection{Abstract Counting}

We define a \textit{memory abstraction} $\powerset{\memset}
\galois{\alpha_\memset}{\gamma_\memset} \absmemset$ as a Galois connection
between sets of concrete memories and abstract memories.  An abstract memory
$\absmem \in \absmemset: \abslocset \finmap \absvalset$ is a finite mapping from
abstract locations to abstract values.  The \textit{strong update} in memory
abstraction is important to increase the precision of static analysis.  For
sound analysis, a memory update for a specific abstract location should join old
abstract values with new abstract values, which calls a \textit{weak update}.
It degrades the analysis precision because of the sprious values.  To overcome
such degradation, researchers proposed the abstract
counting~\cite{abstract-gc-counting, revisit-recency} to track how many times an
abstract location has been allocated and to apply strong updates to singleton
abstract locations.

We extended abstract states with an abstract counting operator $\abscount{-}:
\abslocset \rightarrow \abscountset = \{ \abszero, \absone, \absmany \}$, which
is a function that takes an abstract location and returns its abstract count;
$\abszero$ denotes that it have never been allocated, $\absone$ once, and
$\absmany$ more than equals to twice.

\subsection{On-Demand Access Aanlysis}

### 2020-09-09 paper/pldi21/related.tex
[PLDI21] Removed unnecessary files / Updated formalization

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

The ACM Reference Format text is required for all articles over one
page in length, and is optional for one-page articles (abstracts).

>>>>

\section{Related Work}

\todo

\subsection{Combined Analysis}

\begin{itemize}
  \item Concerto: a framework for combined concrete and abstract
    interpretation~\cite{concerto}
  \item Battles with false positives in static analysis of JavaScript web
    applications in the wild~\cite{battles}
  \item EventHandler-Based Analysis Framework for Web Apps Using Dynamically
    Collected States~\cite{eha}
  \item Automatic Modeling of Opaque Code for JavaScript Static
    Analysis~\cite{opaque-model}
  \item Mimic: Computing models for opaque code~\cite{mimic}
\end{itemize}

\subsection{Abstract Counting}

\begin{itemize}
  \item Improving flow analyses via $\Gamma$CFA: Abstract garbage collection and
    counting~\cite{abstract-gc-counting}
  \item Revisiting recency abstraction for JavaScript: towards an intuitive,
    compositional, and efficient heap abstraction~\cite{revisit-recency}
\end{itemize}

\subsection{Access Analysis}

\begin{itemize}
  \item Access Analysis-Based Tight Localization of Abstract
    Memories~\cite{func-local}
  \item Design and implementation of sparse global analyses for C-like
    languages~\cite{sparse}
\end{itemize}
